On Secure Delegation of SampBQP with a Classical Client

### 2020-03-04 bqp.tex
Fix typo
Add Skype discussion results

	There exists efficient classical poly-time algorithms $\cM_\QHE$ and $\widehat{\QDec_{sk}}$ s.t.
	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement:
	$$\cM_\QHE(\Lambda)=\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$$
	where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and
	$$\widehat{\mathsf{QHE.Dec}_{sk}}\circ\Lambda'=\Lambda\circ\mathsf{QHE.Dec_{sk}}$$
\end{thm}
\begin{prf}
	This proof is by construction.

@@

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
	Observe that the experiments $(\PMFstar, \VMF)(x)$ and $(\Pblindstar, \Vblind(x))$ are identical except for how $w$ is obtained from $\sigma$,
	so by \cref{decodeMeasureOrder} they are equivalent.
	Hence we have $\PMFstar$ with noticeable acceptance probability $\varepsilon$, which is a contradiction.
\end{prf}

@@

\begin{protocol}{Blind $\QPIP_0$ protocol $\Pibz$ for $BQP$ language $L$}
	\label{proto:QPIP0BQP}
	\Ethan{Sync notations on \PiMah}
	\begin{enumerate}
		\item The verifier generates $(pk, sk, ct_x)\leftarrow\cVblind{1}$,
			$\Lambda'\leftarrow\cVblind{2}(x)$,
			and $(k, td)\leftarrow\cVMah{1}(\Lambda')$.
			It sends $k, pk, ct_x$ to the prover.
		\item The prover generates $\sigma\leftarrow\cPblind{1}(pk, ct_x)$ and
			$(y, st)\leftarrow\cPMah{2}(\sigma)$.
			It sends $y$ to the verifier.
		\item The verifier samples public coin $c\leftarrow\set{0, 1}$ and sends it to the prover.
		\item The prover generates and sends $a\leftarrow\cPMah{3}(c, st)$ to the verifier.
		\item If $c=0$, then the verifier generates and outputs $o\leftarrow\cVMah{T}(k, y, a, sk)$.
			Otherwise, it runs $ct_w\leftarrow\cVMah{H}(k, td, y, a, sk)$,
			then generates and outputs $o\leftarrow\cVblind{3}(ct_w, sk, x, \Lambda')$.
	\end{enumerate}
\end{protocol}

@@

\begin{thm}[from \cite{parallelrep, alagic2019twomessage}]
	\label{thm:MFZrep}
	$\PiMFZ$ can be repeated in parallel, obtaining $\PiMFZrep$ that has negligible completeness and soundness errors.
\end{thm}

@@

Here we state our delegation protocol for $\FBQP$.
We do so by breaking an $\FBQP$ instance down into $\BQP$ instances.
Note that our $\BQP$ scheme is one-sided; the prover is allowed to cause the verifier to reject a yes-instance.
As a result, we run two copies of $\Pbzrep$ for every output bit as below:

>>>>

	There exists efficient classical poly-time algorithms $\cM_\QHE$ and $\widehat{\QDec_{sk}}$ s.t.
	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement: \Ethan{Just use basis choice string instead}
	$$\cM_\QHE(\Lambda)=\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$$
	where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and \Ethan{Function compositions feels weird}
	$$\widehat{\mathsf{QHE.Dec}_{sk}}\circ\Lambda'=\Lambda\circ\mathsf{QHE.Dec_{sk}}$$
\end{thm}
\begin{prf}
	This proof is by construction.

@@

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
	Observe that the experiments $(\PMFstar, \VMF)(x)$ and $(\Pblindstar, \Vblind(x))$ are identical except for how $w$ is obtained from $\sigma$,
	so by \cref{decodeMeasureOrder} they are equivalent.
	Hence we have $\PMFstar$ with noticeable acceptance probability $\varepsilon$, which is a contradiction. \Ethan {Write more details; more formula}
\end{prf}

@@

\begin{protocol}{Blind $\QPIP_0$ protocol $\Pibz$ for $\BQP$ language $L$}
	\label{proto:QPIP0BQP}
	\Ethan{Sync notations on \PiMah}
	\begin{enumerate}
		\item The verifier generates $(pk, sk, ct_x)\leftarrow\cVblind{1}$,
			$\Lambda'\leftarrow\cVblind{2}(x)$,
			and $(k, td)\leftarrow\cVMah{1}(\Lambda')$.
			It sends $k, pk, ct_x$ to the prover.
		\item The prover generates $\sigma\leftarrow\cPblind{1}(pk, ct_x)$ and
			$(y, st)\leftarrow\cPMah{2}(\sigma)$.
			It sends $y$ to the verifier.
		\item The verifier samples public coin $c\leftarrow\set{0, 1}$ and sends it to the prover.
		\item The prover generates and sends $a\leftarrow\cPMah{3}(c, st)$ to the verifier.
		\item If $c=0$, then the verifier generates and outputs $o\leftarrow\cVMah{T}(k, y, a, sk)$.
			Otherwise, it runs $ct_w\leftarrow\cVMah{H}(k, td, y, a, sk)$,
			then generates and outputs $o\leftarrow\cVblind{3}(ct_w, sk, x, \Lambda')$.
	\end{enumerate}
\end{protocol}

@@

\begin{thm}[from \cite{parallelrep, alagic2019twomessage}]
	\label{thm:MFZrep}
	$\PiMFZ$ can be repeated in parallel, obtaining $\PiMFZrep$ that has negligible completeness and soundness errors. \Ethan{Just remove this}
\end{thm}

\Ethan{Just define parallel repetition in words}

@@

Here we state our delegation protocol for $\FBQP$.
We do so by breaking an $\FBQP$ instance down into $\BQP$ instances.
Note that our $\BQP$ scheme is one-sided; the prover is allowed to cause the verifier to reject a yes-instance. \Ethan{Explain this better... Write more intuitions. Decision vs function problems; exists vs for all}
As a result, we run two copies of $\Pibzrep$ for every output bit as below:

### 2020-03-04 qpip0.tex
Add Skype discussion results

\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

>>>>

\hannote{comp. indistinguish for subnormalized state?}
\hannote{triangle inequality}

\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

\hannote{$\rho$ is sub normalized}

\hannote{need to simulate one copy?}

For every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp} and $i\in [m]$, consider the following prover strategy for Protocol~\ref{proto:urmila4}: on the first round, try to create $\ket{\psi_{???}}$ \hannote{which $i$ do i use?}
